---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r message=FALSE}
library(tidyverse)
library(readxl)
factor_scores <- read_csv("factor_scores.csv")
SmartWatch_Data_File <- read_excel("SmartWatch Data File.xlsx")
```

```{r}
library(psych)
df <- SmartWatch_Data_File %>%
  cbind(factor_scores[,c(4,5)])
df <- df%>%
  mutate(AmznP = factor(AmznP)) %>%
  mutate(Female = factor(Female)) %>%
  mutate(Degree = factor(Degree)) %>%
  mutate(Income = factor(Income))
```

```{r}
replications(data = df, F1 ~ AmznP*Female*Degree*Income)
```
Note this is an unbalanced design `aov` method is not suit for this...

```{r}
library(nlme)
library(car)
lm(data = df, F1 ~ AmznP*Female*Degree) %>%
  Anova(type = 3) %>%
  print()
```
```{r}
lm(data = df, F2 ~ AmznP*Female*Degree) %>%
  Anova(type = "III")
```
```{r}
lm(data = df, F1 ~ Income) %>%
  Anova(Type = 3)
```


```{r}
aov(data = df, F1 ~ AmznP + Female + Degree + Income) %>%
  summary.lm()

aov(data = df, F1 ~ Female + Degree + Income + AmznP) %>%
  summary.lm()
```

```{r}
aov1 <- aov(data = df, F1 ~ AmznP + Female + Degree + Income) 
aov2 <- aov(data = df, F2 ~ AmznP + Female + Degree + Income) 
summary(aov1)
summary(aov2)
```
"AmznP"  "Female" "Degree" "Income"
```{r}
aov(data = df, F1 ~ Income) %>%
  summary.lm()

```

```{r}
plot(aov1)
```

```{r}
library(ggplot2)
require(gridExtra)
```
Box plot
```{r}
g1.1 <- df %>%
  ggplot(aes(x = AmznP, y = F1)) +
  geom_boxplot() + 
  ylab("F1 - Personal Trainner") + 
  theme_light()
g1.2 <- df %>%
  ggplot(aes(x = Female, y = F1)) +
  geom_boxplot() + 
  ylab(NULL) + 
  theme_light()
g1.3 <- df %>%
  ggplot(aes(x = Degree, y = F1)) + 
  geom_boxplot() + 
  ylab(NULL) + 
  theme_light()
g1.4 <- df %>%
  ggplot(aes(x = Income, y = F1)) + 
  geom_boxplot() + 
  ylab(NULL) + 
  theme_light()

g2.1 <- df %>%
  ggplot(aes(x = AmznP, y = F2)) +
  geom_boxplot() + 
  ylab("F2 - Personal Secretory") + 
  theme_light()
g2.2 <- df %>%
  ggplot(aes(x = Female, y = F2)) +
  geom_boxplot() + 
  ylab(NULL) + 
  theme_light()
g2.3 <- df %>%
  ggplot(aes(x = Degree, y = F2)) + 
  geom_boxplot() + 
  ylab(NULL) + 
  theme_light()
g2.4 <- df %>%
  ggplot(aes(x = Income, y = F2)) + 
  geom_boxplot() + 
  ylab(NULL) + 
  theme_light()

grid.arrange(grobs = list(g1.1, g1.2, g1.3, g1.4,
             g2.1, g2.2, g2.3, g2.4), nrow = 2)
```
violine plot
```{r}
g1.1 <- df %>%
  ggplot(aes(x = AmznP, y = F1)) +
  geom_violin() + 
  ylab("F1 - Sport Band")
g1.2 <- df %>%
  ggplot(aes(x = Female, y = F1)) +
  geom_violin() + 
  ylab(NULL)
g1.3 <- df %>%
  ggplot(aes(x = Degree, y = F1)) + 
  geom_violin() + 
  ylab(NULL)
g1.4 <- df %>%
  ggplot(aes(x = Income, y = F1)) + 
  geom_violin() + 
  ylab(NULL)

g2.1 <- df %>%
  ggplot(aes(x = AmznP, y = F2)) +
  geom_violin() + 
  ylab("F2 - Smart Watch")
g2.2 <- df %>%
  ggplot(aes(x = Female, y = F2)) +
  geom_violin() + 
  ylab(NULL)
g2.3 <- df %>%
  ggplot(aes(x = Degree, y = F2)) + 
  geom_violin() + 
  ylab(NULL)
g2.4 <- df %>%
  ggplot(aes(x = Income, y = F2)) + 
  geom_violin() + 
  ylab(NULL)

grid.arrange(grobs = list(g1.1, g1.2, g1.3, g1.4,
             g2.1, g2.2, g2.3, g2.4), nrow = 2)
```

```{r}
t1 <-t.test(F1 ~ Female, data = df)
t1
```

Explore how income + amazon + two dimension
```{r}
p1 <- df %>%
  ggplot( aes(x = AmznP, y = F1)) +
  geom_boxplot(trim=TRUE) + 
  facet_grid(cols = vars(Income))
p2 <- df %>%
  ggplot( aes(x = AmznP, y = F2)) +
  geom_boxplot(trim=TRUE) + 
  facet_grid(cols = vars(Income))
grid.arrange(p1,p2)
```
amazon prime user who have a stronger 

Female who have Amazon Prime account prefers 
```{r}
p1 <- df %>%
  ggplot( aes(x = AmznP, y = F1)) +
  geom_violin() + 
  facet_grid(cols = vars(Female))
p2 <- df %>%
  ggplot( aes(x = AmznP, y = F2)) +
  geom_violin() + 
  facet_grid(cols = vars(Female))
grid.arrange(p1,p2)
```
Strongest effect is (right conner)... female amazon prime owner showed a stronger preference for ability for sports... 


Higher degree alwalys 
```{r}
aov(data = df, F1 ~ AmznP + Degree) %>%
  summary()
aov(data = df, F2 ~ AmznP + Degree) %>%
  summary()
```
the effect of degree is not as effective as on F1 as on F2. Persue F1 cluster having an amazon account is good factor. Persue F2 target different degree level.


# See if anova and aov print same results..

Even in plus sign order matters...
```{r}
lm(data = df, F1 ~  Female + Degree + Income + AmznP) %>%
  anova()
```

```{r}
aov(data = df, F1 ~ AmznP + Female + Degree + Income) %>%
  summary()
```

```{r}
aov(data = df, F1 ~  Female + Degree + Income + AmznP) %>%
  summary.lm()
```
No using lm method yield same result... but if you print in using anova this would be different 

use `Anova` is different
```{r}
aov(data = df, F1 ~ AmznP + Female + Degree + Income) %>%
  Anova(type = 2)
```

```{r}
aov(data = df, F1 ~ AmznP + Female + Degree + Income) %>%
  summary.lm()
```
`model.tables(type = "mean")`
```{r}
aov(data = df, F1 ~ Female + AmznP + Degree + Income) %>%
  summary.lm()
```


