---
title: "Analysis from Excel only"
author: "Frank Liang"
date: "20/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(tidyverse)
library(readr)
library(plotly)

library(ggalluvial)
#install.packages("ggalluvial")

```

```{r}
AIbyTopic <- read_csv("raw/AIbyTopic.csv")
complete <- read_csv("raw/complete.csv")
```

```{r}
names(AIbyTopic)
AIbyTopic %>%
  select("Region","FundingOrgName","Department","AwardPounds") -> df

df[is.na(df$Region) == FALSE,]
```
Here by Region is not considered because Nah of the data contain "Region" value..

# Alluvium Plot
```{r}
AIbyTopic %>%
  select("FundingOrgName",'ProjectCategory',"LeadROName",'AwardPounds') %>%
  mutate(FundingOrgName = as.factor(FundingOrgName)) %>%
  mutate(LeadROName = as.factor(LeadROName)) %>%
  mutate(ProjectCategory = as.factor(ProjectCategory)) %>%
  ggplot(aes(weight = AwardPounds, axis1 = FundingOrgName, axis2 = LeadROName, fill = ProjectCategory)) + 
  geom_alluvium() + 
  geom_stratum(width = 1/12, fill = "black", color = "white") + 
  #geom_label(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Funding Organisation", "Leading Research Organisations"), expand = c(.05, .05))
  scale_fill_brewer(type = "qual", palette = "Set1")
  
```
use `is_alluvia_form()` to test if data is alluvia form
```{r}
AIbyTopic$FundingOrgName %>% length()
AIbyTopic$LeadROName %>% length()
```

# Explore Statistics of Each Lead RO Universities
```{r}
AIbyTopic %>%
  select(FundingOrgName,ProjectCategory,LeadROName,AwardPounds) %>%
  mutate(FundingOrgName = as.factor(FundingOrgName)) %>%
  mutate(LeadROName = factor(LeadROName)) %>%
  mutate(ProjectCategory = as.factor(ProjectCategory)) %>%
  group_by(LeadROName) %>%
  summarize(sum = sum(AwardPounds), median = median(AwardPounds), mean = mean(AwardPounds)) 
```

, format = "%d/%m/%Y"

```{r}
theme_set(theme_grey())
theme_set(theme(
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_rect(fill = "#f7f7f7"),
          plot.background = element_rect(fill = "white")
        ))


detach("package:ggalluvial", unload=TRUE)
detach("package:plotly", unload=TRUE)
detach("package:tidyverse", unload = TRUE)
detach("package:ggplot2", unload = TRUE)

library(ggplot2)

```

```{r}
AIbyTopic %>%
  dplyr::select(FundingOrgName, LeadROName, AwardPounds, StartDate, EndDate, ProjectReference, Title) %>%
  mutate(StartDate = as.Date(StartDate, format = "%d/%m/%Y")) %>%
  mutate(EndDate = as.Date(EndDate, format = "%d/%m/%Y")) %>%
  mutate(duration = EndDate - StartDate) %>%
  mutate(dailyAward = AwardPounds/as.numeric(duration)) %>%
  ggplot(aes(y = dailyAward, label = LeadROName, label1= Title, label2 = ProjectReference)) + 
  geom_linerange(aes(xmin = StartDate, xmax = EndDate, y = dailyAward), color = "#363636") +
  geom_point(aes(x = StartDate), color = "#363636") + 
  geom_point(aes(x = EndDate), color = "blue") -> g

ggplotly(g)

```
geom_text(label = AIbyTopic$LeadROName, size = 1, color = "black", nudge_x = 15, nudge_y = 50, alpha = 0.5)

Above graph shows that some of data needs to be removed from analysis because those fundings overlap with earch other. 

Which one is more a matter of interest? Number of projects as all? 

```{r}
# Load package
#install.packages("networkD3")
library(networkD3)
 
# Load energy projection data
URL <- "https://cdn.rawgit.com/christophergandrud/networkD3/master/JSONdata/energy.json"
Energy <- jsonlite::fromJSON(URL)

 
# Now we have 2 data frames: a 'links' data frame with 3 columns (from, to, value), and a 'nodes' data frame that gives the name of each node.
head( Energy$links )
head( Energy$nodes )
 
# Thus we can plot it
p <- sankeyNetwork(Links = Energy$links, Nodes = Energy$nodes, Source = "source",
              Target = "target", Value = "value", NodeID = "name",
              units = "TWh", fontSize = 12, nodeWidth = 30)
p
```

```{r}
library(reshape2)
AIbyTopic %>%
  group_by(FundingOrgName) %>%
  summarise(n = n()) %>%
  pull(FundingOrgName) -> FOrg

AIbyTopic %>%
  group_by(LeadROName) %>%
  summarise(n = n()) %>%
  pull(LeadROName) -> ROrg

append(FOrg, ROrg) %>%
  cbind(1:99) %>%
  data.frame() %>%
  rename(id = "V2", names = ".") -> nodes

AIbyTopic %>%
  dplyr::select(FundingOrgName, LeadROName, AwardPounds) %>%
  left_join(nodes, by = c("FundingOrgName" = "names"))  %>%
  rename(source = id) %>%
  left_join(nodes, by = c("LeadROName" = "names")) %>%
  rename(target = id) %>%
  as.data.frame() %>%
  select(source, target, AwardPounds) -> links
    
sankeyNetwork(Links = links, Nodes = nodes, Source = "source", Target = "target", Value = "AwardPounds", NodeID = "names", fontSize = 12, nodeWidth = 30)
```


