---
title: "Clustering Project"
author: "Frank Liang"
date: "17/09/2021"
output: html_document
---
# Load Up
```{r}
library(readr)
library(tidyverse)
library(ggplot2)
library(plotly)

AIbyTopic <- read_csv("raw/AIbyTopic.csv")
complete <- read_csv("raw/complete.csv")

theme_set(theme(
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          panel.background = element_rect(fill = "#f7f7f7"),
          plot.background = element_rect(fill = "white")
        ))
```

## transformation
```{r}
AIbyTopic %>%
  mutate(StartDate = as.Date(StartDate, format = "%d/%m/%Y")) %>%
  mutate(EndDate = as.Date(EndDate, format = "%d/%m/%Y")) %>%
  mutate(duration = EndDate - StartDate) %>%
  mutate(price = AwardPounds/as.numeric(duration)) %>%
  mutate(LeadROName = as.factor(LeadROName)) %>%
  group_by(LeadROName) -> RO
```

## function
```{r}
#define a function to help you look up things in column
lookUp <- function(df, col,term) {
  df <- ungroup(df)
  rgx = paste0("(?i)(",term,")")
  filter(df, str_detect(pull(df, col), rgx))
}
#define function to look up research organisations
RoLookUp <- function(str) {
  lookUp(AIbyTopic,"LeadROName", str) %>%
  pull(GTRProjectUrl) -> url
  if (length(url) == 1) {
    browseURL(url)
  } else 
    lookUp(AIbyTopic,"LeadROName", str) %>%
    select(LeadROName, price, StartDate, EndDate, GTRProjectUrl) 
}
```

# Explore Densities
```{r}
library(htmlwidgets)
AIbyTopic %>%
  mutate(StartDate = as.Date(StartDate, format = "%d/%m/%Y")) %>%
  mutate(EndDate = as.Date(EndDate, format = "%d/%m/%Y")) %>%
  mutate(duration = EndDate - StartDate) %>%
  mutate(price = AwardPounds/as.numeric(duration)) -> df 

cook <- AIbyTopic %>%
  mutate(StartDate = as.Date(StartDate, format = "%d/%m/%Y")) %>%
  mutate(EndDate = as.Date(EndDate, format = "%d/%m/%Y")) %>%
  mutate(duration = EndDate - StartDate) %>%
  mutate(price = AwardPounds/as.numeric(duration))
#write_csv(cook, "raw/cooked.csv")
```

```{r}
# density of price 
df %>%
  filter(price < 10000) %>%
  ggplot(aes(x = price)) +
  geom_density() +
  xlim(0, 600)
```

Cutting Point: 0- 1500: normally distributed beyound is not really

```{r}
# density of durations: shows there are three peak
df %>%
  filter(price < 10000) %>%
  ggplot(aes(x = duration)) +
  geom_density()
# look at institute normalise the data a bit 
df %>%
  filter(price < 10000) %>%
  group_by(LeadROName) %>%
  summarise(duration = mean(duration)) %>%
  ggplot(aes(x = duration)) +
  geom_density()
```

# Interactive Scattor Plot 
```{r}

df %>% 
  #filter(price < 10000) %>% #filter out the weirdly expensive ones 
  ggplot(aes(x = duration, y = price)) +
  geom_point() + 
  geom_hline(yintercept = 10000, alpha = 0.2, col = "blue") + 
  geom_hline(yintercept = 700, alpha = 0.2, col = "blue")-> g
ggplotly(g) %>%
  style(customdata = df$GTRProjectUrl) %>%
  onRender("
    function(el) { 
      el.on('plotly_click', function(d) { 
        var url = d.points[0].customdata;
        window.open(url);
      });
    }
  ") %>%
  style(text = paste0("£",round(df$price*365/1000), " k per year","\n", round(as.numeric(df$duration)/365), " years"))
```

```{r}
# Explore individual 
df %>%
  filter(str_detect(df$LeadROName, "(?i)(Southampton)")) %>%
  ggplot(aes(x = duration)) + 
  geom_density()
```

```{r}
library(cluster)    # clustering algorithms
library(factoextra) # clustering algorithms & visualization


df %>%
  select(price, duration) %>%
  filter(price < 1000) %>%
  na.omit() %>%
  mutate(duration = as.numeric(duration)) %>%
  scale() %>%
  get_dist() -> distMtr

hcl <- hclust(distMtr)
plot(hcl)
rect.hclust(hcl, 5, border = "red")

k <- kmeans(distMtr, centers = 4, nstart = 25) 
fviz_cluster(k, data = distMtr) %>%
  plotly_json()
```

# Map Goe Location Cluster

```{r}
library(leaflet)
library(ggmap)
library(tidygeocoder)
#install.packages("tidygeocoder")
#install.packages("ggmap")
```

API Key: AIzaSyAUIQA9pmYAzqRRSzS5FKer0KdC8zO0NIQ

Don't loss it !!!! Don't share it !!!

```{r}
key = "AIzaSyAUIQA9pmYAzqRRSzS5FKer0KdC8zO0NIQ"
client = "112014706699619003240"
register_google(key, write = TRUE, client = client, account_type = "standard")
```

```{r}
AIbyTopic %>%
  mutate(StartDate = as.Date(StartDate, format = "%d/%m/%Y")) %>%
  mutate(EndDate = as.Date(EndDate, format = "%d/%m/%Y")) %>%
  mutate(duration = EndDate - StartDate) %>%
  mutate(price = AwardPounds/as.numeric(duration)) %>%
  group_by(LeadROName) %>%
  summarise(n = length(LeadROName)) -> LeadRO

#ggmap::geocode(location = LeadRO$LeadROName[1], output = "more")

geocode <- LeadRO %>%
  geocode(LeadROName, method = "arcgis", lat = latitude, long = longtiude)

geocode%>%
  filter(is.na(geocode[,3:4]) == TRUE)
# Allan Tuning Institute was not find correct address
geocode <- geocode %>%
  rows_update(tibble(latitude = 51.530237315026284, longtiude = -0.12726214468233626, LeadROName = "The Alan Turing Institute"), by = "LeadROName") %>%
  rows_update(tibble(latitude = 51.481016045024035, longtiude = -0.2799970412623001, LeadROName = "The National Archives"), by = "LeadROName") %>%
  rows_update(tibble(latitude = 51.403397012011766, longtiude = -0.30359239071764954, LeadROName = "Kingston University"), by = "LeadROName") %>%
  rows_update(tibble(latitude = 53.803533716055156, longtiude = -1.5481857059380568, LeadROName = "Leeds Metropolitan University"), by = "LeadROName") %>%
  rows_update(tibble(latitude = 51.52035059732551, longtiude = -0.1312827581755818, LeadROName = "Institute for Fiscal Studies"), by = "LeadROName") %>%
  rows_update(tibble(latitude = 51.522953345898095, longtiude = -0.12803026930993505, LeadROName = "Institute of Education"), by = "LeadROName") %>%
  rows_update(tibble(latitude = 43.33212325989216, longtiude = -2.9678375334275837, LeadROName = "Basque Centre for Climate Change bc3"), by = "LeadROName") %>%
  rows_update(tibble(latitude = 51.74477519162197, longtiude = -1.4023974580558627, LeadROName = "Diamond Light Source"), by = "LeadROName") %>%
  rows_update(tibble(latitude = 54.01001686525332, longtiude = -2.7862619428703916, LeadROName = "UK Ctr for Ecology & Hydrology fr 011219"), by = "LeadROName")

lookUp(eocode, "LeadROName", "ecology")

Geocode <- geocode %>%
  rename(longitude = longtiude)
write_csv(Geocode, "raw/geocode.csv")
```

The only geocode that has not been found is this: UK Ctr for Ecology & Hydrology fr 011219 4\
54.01001686525332, -2.7862619428703916

```{r}
# insepect if everything is alright
RO %>%
  summarise(x = length(LeadROName)) %>%
  left_join(geocode) -> data
leaflet() %>%
  setView(lat = 55.3781, lng = -3.4360, zoom = 5) %>%
  addProviderTiles("Stamen.TonerLite") %>%
  addCircleMarkers(data = data, lat = ~latitude, lng = ~longtiude,
             stroke = FALSE,
             radius = 5,
             label = paste(data$LeadROName)
             )
```

```{r}
AIbyTopic %>%
  mutate(StartDate = as.Date(StartDate, format = "%d/%m/%Y")) %>%
  mutate(EndDate = as.Date(EndDate, format = "%d/%m/%Y")) %>%
  mutate(duration = EndDate - StartDate) %>%
  mutate(price = AwardPounds/as.numeric(duration)) %>%
  mutate(LeadROName = as.factor(LeadROName)) %>%
  group_by(LeadROName) -> RO
```

```{r}
## Look at number of research projects
RO %>%
  filter(price < 10000) %>%
  summarise(r = length(LeadROName), total = sum(duration)) %>%
  left_join(Geocode) -> data
## Look at how expensive
RO %>%
  dplyr::filter(price < 10000) %>%
  #select(price, LeadROName, Title) %>%
  arrange(-price) %>%
  summarise(number = length(LeadROName), x = mean(price)) %>%
  rows_delete(tibble(LeadROName = "The Alan Turing Institute")) %>% # delete Alan because this affect too much of our analysis
  mutate(r = 50*((x - min(x))/(max(x) - min(x))) + 1) %>%
  left_join(Geocode[, -2], by = ("LeadROName" = "LeadROName")) -> data
## look at project duration
RO %>%
  filter(price < 10000) %>%
  summarise(x = mean(duration)) %>%
  mutate(x = ceiling(as.numeric(x))) %>%
  mutate(r = 20*(( x - min(x))/(max(x) - min(x))) +1) %>%
  left_join(Geocode[, -2]) -> data

```

```{r}
library(leaflet)
leaflet() %>%
  setView(lat = 55.3781, lng = -3.4360, zoom = 5) %>%
  addProviderTiles("Stamen.TonerLite") %>%
  addCircleMarkers(data = data, lat = ~latitude, lng = ~longitude,
             radius = ~r,
             stroke = FALSE,
             label = paste(data$LeadROName #,round(data$x)
                           )
             )
```

# Check some individual RO
```{r}
RO %>%
  lookUp("LeadROName", "basque") %>%
  select(Title,price, StartDate, EndDate)
RO %>%
  lookUp("LeadROName", "delft") %>%
  select(Title,price, StartDate, EndDate)

RoLookUp("basque")
RoLookUp("delft")

RO %>% 
  ggplot(aes(price)) + 
  geom_density() -> g
ggplotly(g)
```

1 WISER: Which Ecosystem Service Models Best Cap... 80.1 2014-01-01 2016-06-30 Same time ended around Brexit

```{r}
data <- RO %>%
  filter(price < 10000)

plot(density(data$AwardPounds))

# cuttail cut everything
data <- RO %>%
  filter(price < 10000) %>%
  filter(AwardPounds < quantile(data$AwardPounds, 0.7))

model <- lm(data = data, AwardPounds ~ duration)  
plot(model)
summary(model)

lm(data = data, AwardPounds ~ duration) 
lm(data = data, AwardPounds ~ StartDate) %>% summary()


lm(data = data, price ~ duration) %>% summary()
lm(data = data, price ~ StartDate) %>% summary()

mean(data$duration, trim = 0.05)/365*12/11
sd(data$duration)
mean(data$price)

data %>%
  ggplot(aes(x = duration, y = AwardPounds)) + 
  geom_point() + 
  geom_smooth()
```

# ANOVA 
```{r}
library(nlme)
library(car)
lm(data = RO, price ~ LeadROName) %>%
  Anova()

# Statistical Significant Within 1000
library(tidyverse)
library(broom)
data <- RO %>%
  filter(price < 10000)
model <- aov(data = data, price ~ LeadROName) 
model %>%
  summary.lm() %>%
  tidy() %>%
  arrange(p.value) %>%
  filter(p.value < 0.05)

```

## cap at 10k
```{r}
data <- RO %>%
  filter(price < 10000) 
data %>%
  group_by(LeadROName) %>%
  summarise(price = mean(price)) %>%
  arrange(-price)

# Statistical Significance. Same result different coding
aov(data = data, price ~ LeadROName) %>%
  summary.lm() %>%
  tidy() %>%
  arrange(p.value) %>%
  filter(p.value < 0.05)

# Duration 
aov(data = data, as.numeric(duration) ~ LeadROName) %>%
  summary.lm() %>%
  tidy() %>%
  arrange(p.value) %>%
  filter(p.value < 0.05)
```
## Cap at 550
```{r}
data <- RO %>%
  filter(price < 550) 
data %>%
  group_by(LeadROName) %>%
  summarise(price = mean(price)) %>%
  arrange(-price)

# Statistical Significance. Same result different coding
aov(data = data, price ~ LeadROName) %>%
  summary.lm() %>%
  tidy() %>%
  arrange(p.value) %>%
  filter(p.value < 0.05) %>%
  select(term, estimate, p.value) %>%
  View()

# Duration 
aov(data = data, as.numeric(duration) ~ LeadROName) %>%
  summary.lm() %>%
  tidy() %>%
  arrange(p.value) %>%
  filter(p.value < 0.05) %>%
  select(term, estimate, p.value) %>%
  View()
```


```{r}
mean(data$price)
sd(data$price)
data %>%
  ggplot(aes(price)) + 
  geom_density() + 
  xlim(0, 550)

# tract grouped data
t1 <- data %>%
  filter(price < 550) %>%
  pull(price)
# tract ungrouped
data %>%
  group_by(LeadROName) %>%
  summarise(price = mean(price)) %>%
  filter(price < 700) %>%
  pull(price) -> t2
t1.2 <- sample(t1, 83) #random sample data
t1.3 <- data %>%
  group_by(LeadROName) %>%
  summarise(price = median(price)) %>%
  filter(price < 550) %>%
  pull(price)

library(boot)
boot(t1)

ggplot() + 
  geom_density(aes(t1.3), col = "blue") + 
  geom_density(aes(t2), col = "red") + 
  geom_vline(xintercept = mean(t1.3), col = "blue", alpha = 0.2) + 
  geom_vline(xintercept = mean(t2), col = "red", alpha = 0.2) + 
  xlab("price")

var.test(t1, t2) # raw compare
var.test(t1.2, t2) #randomly sampled
var.test(t1.3, t2) #sample median only
sd(t1.3)
sd(t1.2)

data <- RO %>%
  filter(price < 550)
```

```{r}
aov(data = data, price ~ LeadROName) %>%
  summary.lm() %>%
  tidy() %>%
  filter(p.value < 0.05) %>%
  arrange(-estimate)

aov(data = data, price ~ LeadROName) %>%
  summary.lm() %>%
  tidy() %>%
  filter(p.value < 0.1 & p.value >= 0.05) %>%
  arrange(-estimate)
```
258.577, 125.8783, 631
334.5311, 162.4008, 83

# what have you done
```{r}
te
```

