---
title: "Duplication Study"
author: "Frank Liang"
date: "01/10/2021"
output: html_document
---
# load up 
```{r}
setwd("~/Dropbox/Projects/Business Project - Topic Modeling")
library(readr)
library(tidyverse)
library(ggplot2)
library(tokenizers)
library(plotly)
library(tidytext)

complete <- read_csv("raw/complete.csv")
AIbyTopic <- read_csv("raw/AIbyTopic.csv")
cooked_csv <- read_csv("raw/cooked.csv")
abstractText <- read_csv("raw/abstractText.csv")

# base function lookup a value
lookup <- function(df, col,term) {
  df <- ungroup(df)
  rgx = paste0("(?i)(",term,")")
  filter(df, str_detect(pull(df, col), rgx))
}
# visualize a project from `cooked_csv`
view_prj <- function(row, term){
lookup(cooked_csv, row, term) -> df
df %>%
  ggplot(aes(y = AwardPounds, label = LeadROName, label1= Title)) + 
  geom_linerange(aes(xmin = StartDate, xmax = EndDate, y = AwardPounds), color = "#363636") +
  geom_point(aes(x = StartDate), color = "#363636") + 
  geom_point(aes(x = EndDate), color = "red") + 
  labs(title = paste("Explore topics")) + 
  geom_text(aes(x = StartDate + duration/2, y = AwardPounds, label = Title), nudge_y = 50, size = 2.5) -> g

ggplotly(g) %>%
  style(traces = 2, text = paste(df$StartDate,"\n",df$duration, "days")) %>%
  style(traces = 1, text = paste(round(df$price),"\n", df$PIFirstName, df$PISurname,"\n",df$duration, "days")) %>%
  style(traces = 3, customdata = df$GTRProjectUrl, text = paste(df$EndDate,"\n", df$LeadROName, "\n",df$Title)) %>%
  onRender("
    function(el) { 
      el.on('plotly_click', function(d) { 
        var url = d.points[0].customdata;
        window.open(url);
      });
    }
  ") # set up click event that open URL
}
# right and left function 
Right <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}
Left <- function(x, n){
  substr(x, 1, n)
}

# visualize by a vector of given id
viz_id <- function(projectReference, text_label = FALSE){
value = paste(rep("ProjectReference ==", each = length(projectReference)), shQuote(projectReference), collapse = " | ")
cooked_csv %>%
    filter(eval(parse(text = value))) -> df
if(text_label == TRUE) {
  #visualisation part
  df %>%
    ggplot(aes(y = AwardPounds, label = LeadROName, label1= Title)) + 
    geom_linerange(aes(xmin = StartDate, xmax = EndDate, y = AwardPounds), color = "#363636") +
    geom_point(aes(x = StartDate), color = "#363636") + 
    geom_point(aes(x = EndDate), color = "red") + 
    labs(title = paste("Explore topics")) + 
    geom_text(aes(x = StartDate + duration/2, y = AwardPounds, label = Title), nudge_y = 50, size = 2.5) -> g
  
  ggplotly(g) %>%
    style(traces = 2, text = paste(df$StartDate,"\n",df$duration, "days")) %>%
    style(traces = 1, text = paste(round(df$price),"\n", df$PIFirstName, df$PISurname,"\n",df$duration, "days")) %>%
    style(traces = 3, customdata = df$GTRProjectUrl, text = paste(df$EndDate,"\n", df$LeadROName, "\n",df$Title)) %>%
    onRender("
      function(el) { 
        el.on('plotly_click', function(d) { 
          var url = d.points[0].customdata;
          window.open(url);
        });
      }
    ") # set up click event that open URL 
  } else { df %>%
      ggplot(aes(y = AwardPounds, label = LeadROName, label1= Title)) + 
      geom_linerange(aes(xmin = StartDate, xmax = EndDate, y = AwardPounds), color = "#363636") +
      geom_point(aes(x = StartDate), color = "#363636") + 
      geom_point(aes(x = EndDate), color = "red") + 
      labs(title = paste("Explore topics")) -> g
    
    ggplotly(g) %>%
      style(traces = 2, text = paste(df$StartDate,"\n",df$duration, "days")) %>%
      style(traces = 1, text = paste(round(df$price),"\n", df$PIFirstName, df$PISurname,"\n",df$duration, "days")) %>%
      style(traces = 3, customdata = df$GTRProjectUrl, text = paste(df$EndDate,"\n", df$LeadROName, "\n",df$Title)) %>%
      onRender("
        function(el) { 
          el.on('plotly_click', function(d) { 
            var url = d.points[0].customdata;
            window.open(url);
          });
        }
      ") # set up click event that open URL
  }
}

  
# find data from id 
  ref_data <- function(vector){
    value = paste(rep("ProjectReference ==", each = length(vector)), shQuote(vector), collapse = " | ")
    
  cooked_csv %>%
    filter(eval(parse(text = value)))
  }
  ref_data(transfered_id)
# filter arguement 
  arg_f <- function(vector, col = "ProjectReference"){
    paste(rep(paste(col, "=="), each = length(vector)), shQuote(vector), collapse = " | ")
}
arg_f(transfered_id)
```
# see some examples 
examples of transfered project 
```{r}
view_prj("Title", "fraud")
```

example of the parallel project? 
```{r}
view_prj("Title", "a unified model of")
```

find out how many unique title are therre
```{r}
left_join(abstractText, cooked_csv, by = c("id" = "ProjectId")) -> df 
df %>%
  select(id, title, AwardPounds, duration) %>%
  group_by(title) %>%
  summarise(n = length(id)) %>%
  filter(n > 1) %>%
  pull(n) %>%
  sum()
```
100 | 235
603 (838 - 235) unique title

find out how many unique abstract text are there
```{r}
df %>%
  group_by(abstractText) %>%
  summarise(n = length(id)) %>%
  filter(n > 1) %>%
  pull(n) %>%
  sum()
```
102 | 246
592 unique content
```{r}
df %>%
  select(id, title, abstractText) %>%
  unique(by= "title")
```

# Select Unique Row and Column Only 
This should be feed into topic modeling but how do you link this to the meta data? 
- can left_join the whole database
```{r}
df %>%
  select(title, abstractText, techAbstractText, potentialImpact) %>%
  unique(na.rm = TRUE)
```
708
add this back on it is 752 

# Transferred Project Versus Parallel Project
potentially use this
```{r}
df %>%
  select(id, title, AwardPounds, duration, StartDate, EndDate) %>%
  group_by(title) %>%
  mutate(n = length(id)) %>%
  filter(n > 1) %>%
  arrange(title, StartDate) %>%
  lookup("title", "SEBASE")

view_prj("Title", "SEBASE")
```

Conditions to be a Transfered Project: 
1. sort all project within the same name by StartDate
2. EndDate of an earlier project is lower than or equal to StartDate of next project
3. earlier project and next project share the same title

Shaffle 
```{r}
AIbyTopic %>%
  group_by(Title) %>%
  mutate(n = length(ProjectReference)) %>%
  filter(n > 1) %>%
  arrange(Title, ProjectReference) -> dup

dup$x = 1:235
dup %>%
  mutate(x = x -1) %>%
  dplyr::select(x, ProjectReference, Title) -> ruler

dup %>%
  left_join(ruler, by = c("x" = "x")) -> pair

pair %>%
  filter(Left(pair$ProjectReference.x, 10)  == Left(pair$ProjectReference.y, 10) & Title.x == Title.y) %>%
  dplyr::select(Title.x, Title.y, ProjectReference.x, ProjectReference.y) -> pair_2

library(reshape2)
pair_2 %>%
  dplyr::select(ProjectReference.x, ProjectReference.y) %>%
  melt(id = c()) %>%
  dplyr::select(value) %>%
  group_by(value) %>%
  summarise(n = length(value)) %>%
  arrange(value) -> transfered

# save files 
write_csv(transfered, "raw/transfered_projects.csv")

transfered %>%
  pull() -> transfered_id

# manual way of find data from a transferred_id data
L = paste(rep("ProjectReference ==", each = length(transfered_id)), shQuote(transfered_id), collapse = " | ")

cooked_csv %>%
  filter(eval(parse(text = L)))

view_prj("Title", "a cognitive")
```


```{r}
ref_data(transfered_id) %>%
  arrange(Title, ProjectReference) %>%
  dplyr::select(ProjectReference, LeadROName, Title, StartDate, EndDate) %>%
  filter(Right(ProjectReference, 1) == "3")

view_prj("Title", "advancing machine learning")
```
 EP/J004049/3     Falmouth Universi… Computational Creativity… 2015-08-01 2017-07-31
 is the only project being transferred twice. 

 
```{r}
ref_data(transfered_id) %>%
  arrange(Title, ProjectReference) %>%
  select(ProjectReference, LeadROName, Title, StartDate, EndDate) %>%
  lookup("Title","advancing machine learning") %>%
  pull(ProjectReference) %>%
  viz_id()

length(transfered_id)
```

# complete paraller projects
```{r}
# filter out transfered project from duplication set = paraller
AIbyTopic %>%
  group_by(Title) %>%
  mutate(n = length(ProjectReference)) %>%
  filter(n > 1) %>%
  filter(!eval(parse(text = arg_f(transfered_id)))) %>%
  arrange(Title) %>%
  dplyr::select(LeadROName, Title, ProjectReference) -> paralleled

write_csv(paralleled, "raw/paralleled_projects.csv")
paralleled %>%
  pull(ProjectReference) -> parallel_id


  #viz_id(text_label = FALSE) 
```

# complete 
```{r}
# method 1: remove two set of prooject
cooked_csv %>%
  filter(!eval(parse(text = arg_f(transfered_id)))) %>%
  filter(!eval(parse(text = arg_f(parallel_id)))) -> singled
# method 2: use `unique()` I don't wanna join

write_csv(singled, "raw/cleaned_unique.csv")
```


```{r}
lookup(complete, "abstractText", "I want to see jackets") %>%
  pull(id) -> id
arg_f(id, "id")

AIbyTopic %>%
  filter(eval(parse(text = arg_f(id, "ProjectId")))) %>%
  pull(ProjectReference) %>%
  viz_id()

```

```{r}
AIbyTopic %>%
  lookup("Title", "Strategic")
```

