---
title: "Topic Modeling From Cleaned Data"
author: "Frank Liang"
date: "11/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
load("RData/enviroment.RData")
arg_f -> arf
library(tidyverse)

viz_thoughts <- function(i, n = 5, nudge = 1*10^4) {
  i = i
  findThoughts(stm_20, topic = c(i), texts =  deep_cleaned$ProjectReference, n = n)[[c(2,1)]] %>%
  viz_id(text_label = T, nudge = nudge)
}

find_thoughts <- function(i, n = 5) {
  findThoughts(stm_20, topic = c(i), texts =  deep_cleaned$ProjectReference, n = n)[[c(2,1)]]
}

stm_thoughts <- function(i){
    findThoughts(stm_20, topic = c(i), texts =  deep_cleaned$Title, n = 3)[[c(2,1)]] %>%
    toString()
}

```

```{r}
AIbyTopic %>%
  filter(!eval(parse(text = arg_f(transfered_id)))) %>%
  filter(!eval(parse(text = arg_f(paralleled_id)))) %>%
  left_join(abstractText, by = c("ProjectId" = "id")) -> cleaned

# there are duplicated abstract text but title are the same
cleaned %>%
  group_by(abstractText) %>%
  mutate(n = length(abstractText)) %>%
  filter(n != 1) %>%
  pull(ProjectReference) -> parallel_plus

# further cleaning
cleaned %>%
  filter(!eval(parse(text = arg_f(parallel_plus)))) -> deep_cleaned
```
We thought data was cleaned but it was not.... 



```{r}
library(quanteda)
library(stm)
deep_cleaned %>%
  dplyr::select(abstractText, X1) %>%
  pull(abstractText) %>%
  textProcessor(metadata = deep_cleaned, 
                lowercase = TRUE,
  removestopwords = TRUE,
  removenumbers = TRUE,
  removepunctuation = TRUE,
  customstopwords = c("develop", "research", "project", "will")
    ) -> cooked

out <- with(cooked, prepDocuments(documents, vocab, meta)) #`document`s is a value output from textProcessor

attach(out)

stm(documents = documents, vocab = vocab, K = 20, data = meta, init.type = "Spectral", verbose = FALSE) -> stm_20

save(stm_20, out, file = "RData/stm_20.RData")
```

```{r}
library(tidytext)
stm_20 %>%
  tidy(matrix = "beta") %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup %>%
  arrange(topic, -beta) %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(x = beta, y = term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) + 
  facet_wrap(~ topic, scales = "free")

toLDAvis(stm_20, documents, R = 10, reorder.topics = FALSE)
```

```{r}
deep_cleaned <- deep_cleaned
#plot(stm_20)
i = 4
findThoughts(stm_20, topic = c(i), texts =  deep_cleaned$Title, n = 5)
findThoughts(stm_20, topic = c(i), texts =  deep_cleaned$ProjectReference, n = 5)[[c(2,1)]] %>%
  viz_id(text_label = T, nudge = 1*10^4)
  
#topicCorr(stm_20) %>% plot() 1 & 6 3 & 10
```

# Meta Data Analysis 
Incorporating topic uncertainty no topic actually have effect 

```{r}
estimateEffect(
  formula = 1:20 ~ AwardPounds, 
  stmobj = stm_20, 
  metadata = meta, 
  uncertainty = "Global") %>%
  tidy() %>%
  filter(p.value < 0.05) %>%
  filter(term != "(Intercept)")

estimateEffect(
  formula = 1:20 ~ AwardPounds, 
  stmobj = stm_20, 
  metadata = meta, 
  uncertainty = "Local", 
  document = documents) %>%
  tidy() %>%
  filter(p.value < 0.05) %>%
  filter(term != "(Intercept)")
```
6 AwardPounds 0.0000000144 0.00000000372      3.89 0.000112
6 AwardPounds 0.0000000143 0.00000000265      5.40 0.0000000990


```{r}
#time and topic
meta %>%
  mutate(StartDate = as.Date(StartDate, format = "%d/%m/%Y")) %>%
  mutate(EndDate = as.Date(EndDate, format = "%d/%m/%Y")) %>%
  mutate(date = StartDate - min(StartDate)) %>%
  mutate(date = as.numeric(date)) %>%
  mutate(duration = EndDate - StartDate) %>%
  mutate(price = AwardPounds/as.numeric(duration)) -> meta_2

estimateEffect(
  formula = 1:20 ~ date, 
  stmobj = stm_20, 
  metadata = meta_2, 
  uncertainty = "Global") %>%
  tidy() %>%
  filter(p.value < 0.01) %>%
  filter(term != "(Intercept)") %>%
  arrange(-estimate) %>% View()
```
> topic term     estimate  std.error statistic  p.value
  <int> <chr>       <dbl>      <dbl>     <dbl>    <dbl>
1     1 date   0.00000969 0.00000362      2.67 0.00770 AI in decision making
2     2 date  -0.0000161  0.00000475     -3.40 0.000728 Data Analytics
3     6 date   0.0000178  0.00000522      3.40 0.000711 Industrial Collaboration Centre
4     8 date   0.0000126  0.00000438      2.87 0.00423 Digital Twins/Urban Analytics
5    11 date  -0.0000170  0.00000479     -3.56 0.000405 Evolutionary Computation
6    20 date  -0.00000948 0.00000365     -2.59 0.00972 Ontology

```{r}
estimateEffect(
  formula = 1:20 ~ price, 
  stmobj = stm_20, 
  metadata = meta_2, 
  uncertainty = "Global") %>%
  tidy() %>%
  filter(p.value < 0.01) %>%
  filter(term != "(Intercept)") %>%
  arrange(-estimate)
```

```{r}
estimateEffect(
  formula = 1:20 ~ sqrt(price), 
  stmobj = stm_20, 
  metadata = meta_2, 
  uncertainty = "Global") %>%
  tidy() %>%
  filter(p.value < 0.01) %>%
  filter(term != "(Intercept)") %>%
  arrange(-estimate)
```


```{r}
estimateEffect(
  formula = 1:20 ~ duration, 
  stmobj = stm_20, 
  metadata = meta_2, 
  uncertainty = "Global") %>%
  tidy() %>%
  filter(p.value < 0.01) %>%
  filter(term != "(Intercept)")
```
> 1     6 duration  0.0000575 0.0000176      3.26 0.00118  
  2     7 duration -0.0000666 0.0000163     -4.08 0.0000504 AI for recreation

```{r}
estimateEffect(
  formula = 1:20 ~ as.factor(LeadROName), 
  stmobj = stm_20, 
  metadata = meta_2, 
  uncertainty = "Global") %>%
  tidy() %>%
  filter(p.value < 0.01) %>%
  mutate(term = str_replace(term, "LeadROName", ""))
```
> # A tibble: 6 x 6
topic term                     estimate std.error statistic  p.value
  <int> <chr>                       <dbl>     <dbl>     <dbl>    <dbl>
1     2 University of Lincoln       0.428     0.157      2.72  6.69e-3 Data Analytic 
2    11 University of Kent          0.360     0.132      2.73  6.56e-3 Evolutionary Computing
3    13 Bangor University           0.844     0.215      3.93  9.72e-5 Robotic and Automation
4    14 University of Abertay D…    0.802     0.290      2.77  5.89e-3 Health
5    17 Diamond Light Source        0.847     0.250      3.39  7.45e-4 Neuronetwork
6    18 Bournemouth University      0.761     0.229      3.33  9.40e-4 Urban Analytic


```{r}
estimateEffect(
  formula = 1:20 ~ LeadROName, 
  stmobj = stm_20, 
  metadata = meta_2, 
  uncertainty = "Local", 
  document = documents) %>%
  tidy() %>%
  filter(p.value < 0.01) %>%
  mutate(term = str_replace(term, "LeadROName", "")) %>%
  filter(term != "(Intercept)") -> topic_org
write_csv(topic_org, "raw/topic and RO.csv")
```

# Explore What Topics
```{r}
toLDAvis(stm_20, documents, R = 10, reorder.topics = FALSE)

stm_20 %>%
  tidy(matrix = "beta") %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup %>%
  arrange(topic, -beta) %>%
  mutate(term = reorder(term, beta)) %>%
  group_by(topic) %>%
  dplyr::summarise(terms = toString(term)) %>%
  mutate(example = find_title(topic)) -> topicTable

write_csv(topicTable, "raw/topicTable.csv")
for(i in c(1:20)){
  find_thoughts(i)
  
}
i = 1
Vectorize(stm_thoughts) -> find_title
```

