---
title: "rx Mutated Variables"
author: "Frank Liang"
date: "09/10/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# Choropleth Graph

Most AI research active organization on a map exclude price higher than
10 k and project that has been transferred. `choropleth.g` choropleth
spikes map

## blackbox

### computation

```{r}
library(rgeos)
library(raster)
library(leaflet)
library(base)
library(sp)
```

```{r}
UK <- getData("GADM", country = "GB", level = 2)
crswgs84 <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

cooked_csv %>% 
  group_by(LeadROName) %>%
  filter(price < 10000) %>% # filter out outliners accroding to
  filter(!eval(parse(text = arg_f(transfered_id)))) %>% # filter out transferred project
  summarise(x = mean(price)) %>% 
  mutate(r = 50*((x - min(x))/(max(x) - min(x))) + 1) %>%
  left_join(geocode) -> data
data %>%
  dplyr::select(longitude, latitude) %>% #long first lat second!
  SpatialPoints(proj4string = crswgs84) -> data_sp

mtrx <- gContains(UK, data_sp, byid = TRUE)

mtrx_r <- colSums(data$r%*%mtrx)/colSums(mtrx)
mtrx_x <- colSums(data$x%*%mtrx)/colSums(mtrx)
mate <- data.frame(id = names(mtrx_r), r = as.numeric(mtrx_r), x = as.numeric(mtrx_x))

UK$c <- mate$r
UK$data <- mate$x
```

### Make Spikes

```{r}
# remove transferred projects 
cooked_csv %>% 
  group_by(LeadROName) %>%
  filter(!eval(parse(text = arg_f(transfered_id)))) %>%
  filter(price < 10000) %>%
  summarise(x = mean(price)) %>%
  mutate(r = 50*((x - min(x))/(max(x) - min(x))) + 1) %>%
  left_join(geocode) -> data

#creat data
rail <- c(1:length(data$x))
plist = c()
w = 0.06
h = 0.1
monitor <- NULL
for (i in rail) {
  la = as.numeric(data[i,5])
  lg = as.numeric(data[i,6])
   hi = sqrt(as.numeric(data[i,3]))
   x_coord <- c(lg - w, lg, lg + w, lg - w)
   y_coord <- c(la, la + h*hi, la, la)
       xym <- cbind(x_coord, y_coord)
       p = Polygon(xym)
      ps = Polygons(list(p), ID = i)
   plist = c(plist, ps)
   
   row = cbind(la, lg)
   monitor = rbind(monitor, row)
}
spike <- sp::SpatialPolygons(plist)

proj4string(spike) = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

plot(spike)
spikes <- SpatialPolygonsDataFrame(spike, data)
```

### Graph Configurations

```{r}
library(plyr)
data %>%
  arrange(-r) %>%
  head(10) %>%
  mutate(LeadROName = revalue(LeadROName, c("The Alan Turing Institute" = "Alan Turing (LND)"))) %>%
  mutate(LeadROName = revalue(LeadROName, c("University of Southampton" = "Southampton"))) %>%
  mutate(LeadROName = revalue(LeadROName, c("University of Bath" = "Bath"))) %>%
  mutate(LeadROName = revalue(LeadROName, c("Newcastle University" = "Newcastle"))) %>%
  mutate(LeadROName = revalue(LeadROName, c("University of Surrey" = "Surrey"))) %>%
  mutate(LeadROName = revalue(LeadROName, c("Heriot-Watt University" = "Heriot-Watt (EB)"))) %>%
  mutate(LeadROName = revalue(LeadROName, c("University of Bristol" = "Bristol"))) %>%
  mutate(LeadROName = revalue(LeadROName, c("University of York" = "York"))) %>%
  mutate(LeadROName = revalue(LeadROName, c("University of Strathclyde" = "Strathclyde (GLA)"))) %>%
  rows_delete(tibble(LeadROName = "Royal Veterinary College")) -> text_label

text_label %>%
  rows_delete(tibble(LeadROName = "Heriot-Watt (EB)")) %>%
  rows_delete(tibble(LeadROName = "Strathclyde (GLA)")) -> text_label1

text_label %>%
  filter(LeadROName == "Heriot-Watt (EB)" | LeadROName ==  "Strathclyde (GLA)") %>%
  rows_update(tibble(LeadROName = "Heriot-Watt (EB)", longitude = -2) ) %>%
  rows_update(tibble(LeadROName = "Strathclyde (GLA)", longitude = -5) ) -> text_label2
```

```{r}
mypal <- colorNumeric(palette = "OrRd", domain = UK$data, na.color = "transparent")
mypal_2 <- colorNumeric(palette = "OrRd", domain = sqrt(spikes$x), na.color = "transparent")
text_style <- list(
        "color" = "black",
        "font-family" = "Futura",
        "font-style" = "bold",
        "text-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "text-outline" = "white"
      )
leaflet() %>% 
  setView(lat = 55.3781, lng = -3.4360, zoom = 5) %>% 
  addProviderTiles(providers$CartoDB.PositronNoLabels) %>% 
  addPolygons(data = UK, stroke = TRUE, 
              fillColor = ~mypal(data),
              fillOpacity = 0.6, col = "black", weight = 0.4,
              highlightOptions = highlightOptions(opacity = 1,
                                                  weight = 1.5,
                                                  bringToFront = FALSE),
              label = paste(UK$NAME_2, round(UK$data))
  ) %>%
  addLegend("bottomright", pal = mypal, values = UK$data, labFormat = labelFormat(prefix = "£/d "), opacity = 1) %>%
  addPolygons(data = spikes, col = "black", stroke = TRUE, fillColor = ~mypal_2(sqrt(x)), fillOpacity = 1, weight = 1, opacity = 0.75,
              highlightOptions = highlightOptions(fillOpacity = 2,
                                                  weight = 2,
                                                  bringToFront = TRUE),
              label = paste(spikes$LeadROName, "£/d", round(spikes$x))
              )  %>%
  addLabelOnlyMarkers(data = text_label1, label = ~LeadROName, lat = ~latitude, lng = ~longitude, labelOptions = labelOptions(noHide = T, textsize = "12px", textOnly = TRUE,
                                         direction =  "top", opacity = 0.7,
                                         style = text_style), halo = TRUE, hc = "white"
        ) %>%
   addLabelOnlyMarkers(data = text_label2, label = ~LeadROName, lat = ~latitude, lng = ~longitude, labelOptions = labelOptions(noHide = T, textsize = "12px", textOnly = TRUE, 
                                         direction =  "top", opacity = 0.7,
                                         style = text_style)
        ) 
```

# Explore the Transfered Project

Output in this section: `net_flow` see three visualisation: `network.g`
visualise network `inflow.g` visualise number of project transfered into
RO, marked by red `outflow.g` visualise number of project transfered out
of RO, marked by blue

## Blackbox

### pair transfered projects

```{r}
# transfered project in pairs `pair_2` should be a from_to 
AIbyTopic %>%
  group_by(Title) %>%
  mutate(n = length(ProjectReference)) %>%
  filter(n > 1) %>%
  arrange(Title, ProjectReference) -> dup
dup$x = 1:235
dup %>%
  mutate(x = x -1) %>%
  dplyr::select(x, ProjectReference, Title) -> ruler
dup %>%
  left_join(ruler, by = c("x" = "x")) -> pair
pair %>%
  filter(Left(pair$ProjectReference.x, 10) == Left(pair$ProjectReference.y, 10) & Title.x == Title.y) %>%
  dplyr::select(Title.x, Title.y, ProjectReference.x, ProjectReference.y) -> pair_2

AIbyTopic %>% 
  dplyr::select(LeadROName, ProjectReference) -> id

AIbyTopic %>% 
  filter(eval(parse(text = arg_f(transfered_id)))) %>%
  dplyr::select(LeadROName) %>%
  group_by(LeadROName) %>%
  summarise(n = length(LeadROName)) %>%
  mutate(x = 1:length(LeadROName)) %>%
  left_join(geocode, by = c("LeadROName" = "LeadROName")) %>%
  rename(id = x) %>% dplyr::select(id, LeadROName, latitude, longitude) -> node_raw

pair_2 %>%
  left_join(id, by = c("ProjectReference.x" = "ProjectReference")) %>%
  rename(from = LeadROName) %>%
  left_join(id, by = c("ProjectReference.y" = "ProjectReference")) %>%
  rename(to = LeadROName) %>%
  dplyr::select(from, to, ProjectReference.x, ProjectReference.y, Title.x) %>%
  rename(title = Title.x) %>% 
  left_join(node_raw, by = c("from" = "LeadROName")) %>%
  rename(from_id = id) %>%
  left_join(node_raw, by = c("to" = "LeadROName")) %>%
  rename(to_id = id) %>%
  dplyr::select(from_id, to_id, ProjectReference.y, ProjectReference.x) %>%
  rename(from = from_id) %>% rename(to = to_id) -> edge
```

### Network Visualisation

```{r}
library(igraph)
library(visNetwork)

nodes <- node_raw %>%
  rename(label = LeadROName)

visNetwork(nodes, edge) %>%
  visEdges(shadow = TRUE,
           arrows =list(to = list(enabled = TRUE, scaleFactor = 2))) -> network.g
```

### Compute Netflow

```{r}
edge %>% left_join(node, by = c("from" = "id")) %>%
  rename(lat_from = latitude) %>% rename(lng_from = longitude) %>%
  left_join(node, by = c("to" = "id")) %>%
  rename(lat_to = latitude) %>% rename(lng_to = longitude) -> edges

stand <- function(v) {
  (v - min(v) + 1)/(max(v) - min(v) + 1)
}

# compute netflow for each node
edge %>%
  group_by(to) %>%
  mutate(r1 = length(to)) %>%
  ungroup() %>%
  group_by(from) %>%
  mutate(r2 = length(to)) %>%
  ungroup() -> from_to
from_to %>%
  dplyr::select(from, r2) -> from_r2
from_to %>%
  dplyr::select(to, r1) -> to_r1
to_r1 %>% full_join(from_r2, by = c("to" = "from")) %>%
  mutate(r2 = replace(r2, is.na(r2), 0)) %>%
  mutate(r1 = replace(r1, is.na(r1), 0)) %>%
  mutate(n = r1 - r2) %>%
  rename(id = to) %>% 
  group_by(id) %>%
  summarise(n = mean(n))-> net_flow
```


```{r}
# inflow map 
token = "pk.eyJ1IjoiZmxpYW5ndWsiLCJhIjoiY2t1Z3dkYXJ4MXI3ZDMybXR1czhjMnN3YSJ9.h8KmaN_vC0whFf34x1m84Q"
Sys.setenv("MAPBOX_TOKEN" = token)

node_raw %>%
  left_join(to_r1, by = c("id" = "to")) %>%
  rename(r = r1) -> node_inflow

plot_mapbox() %>%
  add_markers(data = node_outflow, x = ~longitude, y = ~latitude, 
              color = I("red"), 
              text = ~LeadROName, alpha = 0.4,
              hoverinfo = "text",size = ~r) %>%
  add_segments(data = edges, 
    x = ~lng_from, xend = ~lng_to,
    y = ~lat_from, yend = ~lat_to, 
    alpha = 0.3, size = I(1), color = I("red"), hoverinfo = "none"
    ) %>%
  layout(mapbox = list(
    style = "dark",
    zoom = 4.2, 
    center = list(lat=54.3781, lon=-3.4360)
  )) -> inflow.g
```

```{r}
# outflow map
node_raw %>%
  left_join(from_r2, by = c("id" = "from")) %>% #just change id to to from
  rename(r = r2) %>%
  mutate(r = replace(r, is.na(r), 0)) -> node_outflow

plot_mapbox() %>%
  add_markers(data = node_outflow, x = ~longitude, y = ~latitude, 
              color = I("blue"), 
              text = ~LeadROName, alpha = 0.5,
              hoverinfo = "text",size = ~r) %>%
  add_segments(data = edges, 
    x = ~lng_from, xend = ~lng_to,
    y = ~lat_from, yend = ~lat_to, 
    alpha = 0.3, size = I(1), color = I("blue"), hoverinfo = "none"
    ) %>%
  layout(mapbox = list(
    style = "dark",
    zoom = 4.2, 
    center = list(lat=54.3781, lon=-3.4360)
  )) -> outflow.g
```

```{r}
# combine both
plot_mapbox() %>%
  add_segments(data = edges, 
    x = ~lng_from, xend = ~lng_to,
    y = ~lat_from, yend = ~lat_to, 
    alpha = 0.1, size = I(1), color = I("red"), hoverinfo = "none"
    ) %>%
  add_markers(data = node_inflow, x = ~longitude, y = ~latitude, 
              color = I("red"), 
              text = ~LeadROName, alpha = 0.5,
              hoverinfo = "text",size = ~r^2) %>%
  add_markers(data = node_outflow, x = ~longitude, y = ~latitude, 
              color = I("black"), 
              text = ~LeadROName, alpha = 0.5,
              hoverinfo = "text",size = ~r^2) %>%
  layout(mapbox = list(
    style = "dark",
    zoom = 4.2, 
    center = list(lat=54.3781, lon=-3.4360)
  )) -> flowmap.g
```

# Project Overview

one that filter out transferred project `overview_by_price.g`
`overview_by_award.g` 
## Configuration Box

```{r}
AIbyTopic %>%
  mutate(StartDate = as.Date(StartDate, format = "%d/%m/%Y")) %>%
  mutate(EndDate = as.Date(EndDate, format = "%d/%m/%Y")) %>%
  mutate(duration = EndDate - StartDate) %>%
  mutate(price = AwardPounds/as.numeric(duration)) %>%
  filter(!eval(parse(text = arg_f(transfered_id)))) -> df

df %>%
  ggplot(aes(y = price, label = LeadROName, label1= Title, label2 = ProjectReference)) + 
  geom_linerange(aes(xmin = StartDate, xmax = EndDate, y = price), color = "#363636") +
  geom_point(aes(x = StartDate), color = "#363636") + 
  geom_point(aes(x = EndDate), color = "blue") -> g

ggplotly(g) %>%
  style(traces = 2, text = paste(df$StartDate,"\n",df$duration, "days")) %>%
  style(traces = 1, text = paste( df$PIFirstName, df$PISurname,"\n",df$duration, "days")) %>%
  style(traces = 3, customdata = df$GTRProjectUrl, text = paste(df$EndDate,"\n", df$LeadROName, "\n",df$Title)) %>%
  onRender("
    function(el) { 
      el.on('plotly_click', function(d) { 
        var url = d.points[0].customdata;
        window.open(url);
      });
    }
  ") -> overview_by_price.g #set up click event that open URL
```

```{r}
AIbyTopic %>%
  mutate(StartDate = as.Date(StartDate, format = "%d/%m/%Y")) %>%
  mutate(EndDate = as.Date(EndDate, format = "%d/%m/%Y")) %>%
  mutate(duration = EndDate - StartDate) %>%
  mutate(price = AwardPounds/as.numeric(duration)) -> df

df %>%
  ggplot(aes(y = AwardPounds, label = LeadROName, label1= Title, label2 = ProjectReference)) + 
  geom_linerange(aes(xmin = StartDate, xmax = EndDate, y = AwardPounds), color = "#363636") +
  geom_point(aes(x = StartDate), color = "#363636") + 
  geom_point(aes(x = EndDate), color = "#e8516f") -> g

ggplotly(g) %>%
  style(traces = 2, text = paste(df$StartDate,"\n",df$duration, "days")) %>%
  style(traces = 1, text = paste( df$PIFirstName, df$PISurname,"\n",df$duration, "days")) %>%
  style(traces = 3, customdata = df$GTRProjectUrl, text = paste(df$EndDate,"\n", df$LeadROName, "\n",df$Title)) %>%
  onRender("
    function(el) { 
      el.on('plotly_click', function(d) { 
        var url = d.points[0].customdata;
        window.open(url);
      });
    }
  ") -> overview_by_award.g #set up click event that open URL
overview_by_award.g
```

# Show Density if Durationa and Award Pounds
```{r}
library(ggExtra)
df <- cooked_csv
df %>% 
  filter(!eval(parse(text = arg_f(transfered_id)))) %>% #filter out the weirdly expensive ones 
  ggplot(aes(x = duration, y = price)) +
  geom_point() + 
  geom_hline(yintercept = 10000, alpha = 0.2, col = "blue") + 
  geom_hline(yintercept = 700, alpha = 0.2, col = "blue") -> g
  
ggMarginal(g) -> marginal
```


```{r}
save(overview_by_award.g,
     overview_by_price.g, 
     net_flow,
     network.g,
     inflow.g,
     outflow.g,
     flowmap.g,
     choropleth.g, file = "RData/vis.RData")
```

```{r}
flowmap.g
network.g
net_flow %>% arrange(-n) %>%
  left_join(unique(node), by = c("id" = "id"))
```

