---
title: "For Operation Analysis"
author: "Frank Liang"
date: "22/04/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("rDEA")
library("dplyr")
#install.packages("rDEA")
library("ggplot2")
library("plotly")
library("readr")
```

```{r}
DEA <- read_csv("./DEA.csv")

DEA$`average pay` <- gsub("\\$", '', DEA$`average pay`)
DEA$`average pay` <- gsub("\\s",'', DEA$`average pay`)
DEA$`average pay` <- gsub(",",'', DEA$`average pay`)
DEA$`average pay` <- as.numeric(DEA$`average pay`)

```

# Project 1: DEA analysis
b. calculate efficiency score without tuition fee
```{r}
x <- DEA[,3:4]
y <- DEA[,5:6]

dea <- dea(XREF=x, YREF=y, X=x, Y=y, model="input", RTS="constant")
DEA$efficiency_b <- dea$thetaOpt

DEA
DEA$efficiency_b
```

c.1 calculate efficiency score with tuition fee without derive dimension 
```{r}
X <- DEA[,2:4]
Y <- DEA[,5:6]

di_naive = dea(XREF=X, YREF=Y, X=X, Y=Y, model="input", RTS="constant")
DEA$efficiency_c <- di_naive$thetaOpt

DEA[,c(1,8)]
```

 
```{r}

fon <- cbind(DEA[,2]/(DEA[,6]*DEA[,5]), DEA[,3]*DEA[,4]/(DEA[,6]*DEA[,5]))
names(fon)[1] <- "input_1"
names(fon)[2] <- "input_2"

with(fon, plot(x = input_1, y = input_2, type = "p"))

fon <- cbind(fon, DEA[,c(1,7,8)])

```

Use `ggplot`
```{r}

names(fon)[names(fon) == "X1"] <- "uni" 

eff <- fon[fon$efficiency_c == 1, 1:3]

fon[,c(3,5)]


p <- ggplot(fon, aes(x= input_1, y= input_2, text = uni)) +
       geom_point(shape=1) +
    geom_point(data = eff, color = "blue")
    
ggplotly(p)
```


c.2.1 calculate efficiency score with tuition fee without derive dimension 
```{r}
# derive dimension
x <- cbind(DEA[,2], DEA[,3]*DEA[,4])
y <- DEA[,5]*DEA[,6]
  
trans <- dea(XREF <- x, YREF <- y, X = x, Y = y, model = "input", RTS="constant")

# cbind data to fon
fon <- cbind(fon, trans$thetaOpt)
fon[,c(3,6)]
```

c.2.2 ploting via ggplot
```{r echo=TRUE}
# plot
names(fon)[1] <- "x"
names(fon)[2] <- "y"
eff2 <- fon[fon$`trans$thetaOpt` == 1, 1:3]
g <- ggplot(fon, aes(x = x, y = y, label = uni)) +
  geom_point(shape = 1) +
  geom_point(data = eff2, color = "blue") + 
  labs(x = "tuition fee", y = "competitivness")

ggplotly(g)
```
please find HTML output in folder

# Project 3


```{r}
library(tidyverse)
library(network)

# create network object
edge <- tibble(from = c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4, 5, 5, 6), 
               to = c(2, 3, 4, 5, 4, 3, 4, 5, 6, 5, 6, 6, 7, 7),
               cap = c(1, 5, 2, 4, 1, 2, 3, 6, 8, 3, 7, 5, 2, 6))
node <- tibble(id = 1:7)

nw <- network(edge, vertex.attr = node, matrix.type = "edgelist", ignore.eval = FALSE)
plot(nw, vertex.cex = 4)

nw
```
`plot` use `Fruchterman and Reingold algorithm` to decide on the placement of the nodes.


```{r}
detach(package:network)
#rm(routes_network)
library(igraph)
install.packages("visNetwork")
library(visNetwork)
```
computing max flow
```{r}
igph <- graph_from_data_frame(d = edge, vertices = node, directed = TRUE)
max <- graph.maxflow(igph, source = 1, target = 7, capacity = edge$cap)
max$flow


shortest_paths(igph, from = 1, to = 7, )

```
Visualisation

note: `edges` `nodes` are object created for the purpose of visualization. Raw data are preserved in object `edge` and `node`. 
```{R}
edges <- edge %>% 
  mutate(flow = max$flow) %>%
  mutate(dashes = flow == 0) %>%
  mutate(shadow = flow != 0) %>%
  mutate(width = flow/3 + 1) %>%
  mutate(label = flow)
  

nodes <- node %>%
  mutate(label = id) %>%
  mutate(shape = c("circle"))

nodes

visNetwork(nodes, edges) %>%
  visIgraphLayout(layout = "layout_with_fr")  %>%
  visEdges(arrows = "to", color = list(color = "lightblue",
                                       highlight = "powderblue",
                                       hover = "powderblue")) %>%
  visNodes(size = 20, color = list(background = "lightblue", 
                                   highlight = "coral", 
                                   border = "lightblue",
                                   hover = "coral"),
           font = list(color = "white",size = 14, strokeWidth = 1, align = "center")
           ) %>%
  visOptions( highlightNearest = list(enabled = TRUE, hover = TRUE))

```

longest path
```{r}
edge.b <- mutate(edge, new_cap = max(cap) - cap + 1)
igph.b <- graph_from_data_frame(d = edge.b, vertices = node, directed = TRUE)

e <- all_simple_paths(igph.b, from = 1, to = 7) 
e <- list(1, 3, 5, 6, 7)
```

```{r}
path <- e %>%
  unlist() %>%
  matrix(nrow = length(e), byrow = "FALSE") %>%
  data.frame() %>%
  mutate(color = "coral")
nodes.c <- node %>%
  mutate(label = id) %>%
  mutate(shape = c("circle")) %>%
  left_join(path, copy = TRUE, by = c("id" = "."))

path2 <- edge[c(2, 8, 12, 14),] %>%
  mutate(color = "coral") %>%
  mutate(shadow = TRUE)
edges.c <- edge %>%
  mutate(label = cap) %>%
  left_join(path2) 
visNetwork(nodes.c, edges.c)  %>%
  visIgraphLayout(layout = "layout_with_fr")  %>%
  visEdges(arrows = "to", color = list(color = "lightblue",
                                       highlight = "powderblue",
                                       hover = "powderblue")) %>%
  visNodes(size = 20, color = list(background = "lightblue", 
                                   highlight = "coral", 
                                   border = "lightblue",
                                   hover = "coral"),
           font = list(color = "white",size = 14, strokeWidth = 1, align = "center")
           ) %>%
  visOptions( highlightNearest = list(enabled = TRUE, hover = TRUE))
```
```{r}
edge[, c(1,2)] == c(1,2)
edge[c(2, 8, 12, 14),]
```





